Budgeted Reinforcement Learning in Continuous State Space

### 2019-05-27 main.tex
Updates from Overleaf

When the BMDP is unknown, we need to adapt \Cref{algo:bvi} to work with a batch of samples $\cD=\{(\os_i,\oa_i,r_i,\os_i'\}_{i\in [0,N]}$ collected by interaction with the environment. Applying $\cT$ in \eqref{eq:bellman-optimality} would require computing an expectation $\expectedvalue_{\os'\sim \ov{P}}$ over next states $\os'$ and hence an access to the model $\ov{P}$. We instead use $\hat{\cT}$, a sampling operator, in which this expectation is replaced by:
\begin{equation*}
    \hat{\cT} Q(\os_i, \oa_i, r_i, \os'_i) \eqdef r_i + \gamma \sum_{\ov{a'_i}\in \cA_i} \pi_\text{greedy}(\ov{a'_i}|\ov{s'_i}; Q) Q(\ov{s'_i}, \ov{a'_i}).
\end{equation*}
We introduce in \Cref{algo:bftq} the \emph{Budgeted-Fitted-Q} (BFTQ) algorithm, an extension of the \emph{Fitted-Q} (\FTQ) algorithm \citep{Ernst2005,Riedmiller2005} adapted to solve unknown BMDPs. Because we work with  continuous state space $\cS$ and budget space $\cB$, we need to employ function-approximation in order to generalise to nearby states and budgets. Precisely, given a parametrized model $Q_\theta$, we seek to minimise a regression loss $\cL(Q_\theta, Q_\text{target};\cD) = \sum_{\cD} ||Q_\theta(\os, \oa) - Q_\text{target}(\os, \oa, R, \os')||_2^2$.
Any model can be used, such as linear models, regression trees, or neural networks.

>>>>

When the BMDP is unknown, we need to adapt \Cref{algo:bvi} to work with a batch of samples $\cD=\{(\os_i,\oa_i,r_i,\os_i'\}_{i\in [0,N]}$ collected by interaction with the environment. Applying $\cT$ in \eqref{eq:bellman-optimality} would require computing an expectation $\expectedvalue_{\os'\sim \ov{P}}$ over next states $\os'$ and hence an access to the model $\ov{P}$. We instead use $\hat{\cT}$, a sampling operator, in which this expectation is replaced by:
\begin{equation*}
    \hat{\cT} Q(\os_i, \oa_i, r_i, \os'_i) \eqdef r_i + \gamma \sum_{\ov{a'_i}\in \cA_i} \pi_\text{greedy}(\ov{a'_i}|\ov{s'_i}; Q) Q(\ov{s'_i}, \ov{a'_i}).
\end{equation*}
We introduce in \Cref{algo:bftq} the \emph{Budgeted-Fitted-Q} (BFTQ) algorithm, an extension of the \emph{Fitted-Q} (\FTQ) algorithm \citep{Ernst2005,Riedmiller2005} adapted to solve unknown BMDPs. Because we work with  continuous state space $\cS$ and budget space $\cB$, we need to employ function-approximation in order to generalise to nearby states and budgets. Precisely, given a parametrized model $Q_\theta$, we seek to minimise a regression loss $\cL(Q_\theta, Q_\text{target};\cD) = \sum_{\cD} ||Q_\theta(\os, \oa) - Q_\text{target}(\os, \oa, r, \os')||_2^2$.
Any model can be used, such as linear models, regression trees, or neural networks.
